%Abstract Page 
\hbox{\ }

\renewcommand{\baselinestretch}{1}
\small \normalsize

\begin{center}
\large{{ABSTRACT}} 

\vspace{3em} 

\end{center}
\hspace{-.15in}
\begin{tabular}{ll}
Title of dissertation:    & {\large  Phase mixing in Turbulent}\\
&                          {\large   Magnetized Plasmas } \\
\ \\
&                          {\large  Anjor Vishwas Kanekar, } \\
&                          {\large  Doctor of Philosophy, 2014 } \\
\ \\
Dissertation directed by: & {\large  Professor William Dorland} \\
&  				{\large	 Department of Physics } \\
\end{tabular}

\vspace{3em}

\renewcommand{\baselinestretch}{2}
\large \normalsize

Landau damping (phase mixing) is perhaps the most salient feature of weakly collisional 
plasmas. Phase mixing plays a crucial role in kinetic plasma turbulence---it transfers
energy to small velocity space scales, and provides a route to dissipation to the
turbulent cascade. Phase mixing has been well understood in the linear limit for nearly
seventy years, however, we do not yet fully understand the behavior of phase mixing
in presence of a fluid-like turbulent cascade---a common scenario in weakly
collisional systems.

In this thesis, we consider simple models for kinetic passive scalar turbulence that simultaneously incorporate
phase mixing and turbulent cascade, in order to study the effects of turbulence on phase mixing.
 We show that the nonlinear cascade scatters energy in the phase space
so as to generate a turbulent version of the plasma echo.
We find that this \textit{stochastic
plasma echo} suppresses phase mixing by reducing the net flux to
small velocity space scales.

Further, we study the problem of compressive fluctuations in the solar wind at scales
larger than the ion Larmor radius (the so-called inertial range). The compressive
perturbations at these scales are passively mixed by the Alfv\'{e}nic turbulence. Hence, the general results
regarding kinetic passive scalar turbulence are directly applicable to this problem. We
find that the suppression of phase mixing by the stochastic plasma echo is key to the persistence of
the turbulent cascade of compressive fluctuations at scales where these
fluctuations are expected to be strongly damped.

A new code, \Gand\ was developed for the GPU architecture using the CUDA platform in order to study
these systems, in particular to study solar wind turbulence
in the inertial range. 
