%Acknowledgments

\renewcommand{\baselinestretch}{2}
\small\normalsize
\hbox{\ }
 
\vspace{-.65in}

\begin{center}
\large{Acknowledgments} 
\end{center} 

I am deeply grateful to my advisor, Prof. William Dorland. Bill has been a tremendous
support, as a physicist, and more importantly, as a friend. None of this work could have
been possible without his help. I am indebted to Prof. Alexander Schekochihin who played a
vital role in the completion of this thesis. I have learned a lot from Alex, and hope to
continue doing so in coming years. I am thankful to the extended research-family I have been fortunate enough to be a part of. This includes Dr. Nuno Loureiro, Prof.
Greg Hammett, Prof. Steven Cowley, Dr. Ian Abel, Dr. Edmund Highcock, George Wilkie, Wrick Sengupta,
Dr. Jason TenBarge, Prof.
Greg Howes, Dr. Matthew Kunz, Prof. Michael Barnes, Dr. Gabe Plunk, Prof. Felix Parra, Prof. Tomo Tatsuno,
Prof. Ryusuke Numata, among others. I would like to specially mention ``the
tome"\cite{tome}, a paper which started me off on the path of plasma physics.

I have benefited considerably from the support of my friends and colleagues in
Maryland---Jonathan Hoffman, Matthew Reed, Kristen Voigt, Evan Berkowitz, Eric Kuo, David
Green, Shane Squires to name a few. Rufus Reed deserves a special mention in this category
for being the most affectionate Vizsla, who often cheered me up when it was required.

Finally, I am eternally thankful to my loving and supportive wife, Jui. This dissertation
would not have been possible without her support.

\vspace{1ex}

